KDM5C is a sex-biased brake against germline gene expression programs in somatic lineages

### 2024-11-08 submission/manuscript.Rmd
add competing interest section

## Data availability
### WGBS in wild-type and _Kdm5c_-KO ESCs and exEpiLCs
Raw fastq files are deposited in the Sequence Read Archive (SRA) https://www.ncbi.nlm.nih.gov/sra under the bioProject PRJNA1165148. https://www.ncbi.nlm.nih.gov/bioproject/PRJNA1165148

@@

>>>>

## Data access
### WGBS in wild-type and _Kdm5c_-KO ESCs and exEpiLCs
Raw fastq files are deposited in the Sequence Read Archive (SRA) https://www.ncbi.nlm.nih.gov/sra under the bioProject PRJNA1165148. https://www.ncbi.nlm.nih.gov/bioproject/PRJNA1165148

@@

# Competing Interest
S.I. is a member of the Scientific Advisory Board of KDM5C Advocacy, Research, Education & Support (KARES). All other authors declare no conflict of interest.
